---
title: "Machine Learning Course Project"
output: html_document
---

The goal of your project is to predict the manner in which subjects did a physical exercise, based on physical measurements.

```{r}
setwd("C:\\Users\\Oleg\\Documents\\coursera\\courses\\08_PracticalMachineLearning\\project")
library(caret)
dat <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
```

Filter out variables that are mostly NA, or are factors, or are not related to measured variables, i.e. arm/forarm/dumbell.  The lda model is used because the data is largely numeric measurements, and it is computationally convenient.  The confusion matrix is used to see the accuracy and kappa.

Cross validation can be used to reduce overfitting, i.e. not relying on error estimates from the training set.  Because there are a large number of parameters, we increase the number cross validation samples.  Leave one out cross validation uses as many samples are there are observations.


```{r}
largely.na=sapply(dat, function(x) sum(is.na(x))/length(x) > .5 | class(x)=="factor") |
!grepl("arm|belt|dumbbell", names(dat),T)
largely.na=names(largely.na)[largely.na] 
dat1=dat[, - match(largely.na, names(dat))]

modelFit <-  train(dat$classe ~.,data=dat1, method="lda", trainControl="LOOCV")
predictions = predict(modelFit, newdata=dat1)
confusionMatrix(predictions, dat$classe)
```

The accuracy is 70% in sample.

Finally, make predictions on the test data.  Classe is not available, so out of sample performance is not known

```{r}
predictions = predict(modelFit, newdata=testing)
```
 
The data used was

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013. 
